%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  {Senior Software Engineer}
  {PT Bank Danamon Tbk. (D-Bank PRO)}
  {Central Jakarta, Indonesia}
  {Jun. 2023 --- Present}
  {
    \begin{cvitems}
      \item {Develop back-end applications with Node.js and PostgreSQL and front-end applications with Angular, React, and Apache Cordova}
      \item {Developed and released new Cash-out via partner feature in D-Bank PRO}
      \item {Initialized and released new Backoffice app based on Strapi and enhance marketing contents on the app to be dynamic}
      \item {Initialized new feature of Gold Saving investment in DBank-PRO}
      \item {Designed the end-to-end architecture for the new Backoffice app for DBank-PRO}
      \item {Initialized code lint and unit testing in front-end and back-end repositories}
      \item {Integrated native C++ library to Android app and Apache Cordova plugin with Angular source code}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Technical Lead}
    {PT Bank BTPN Tbk. (Jenius)}
    {South Jakarta, Indonesia}
    {Jul. 2021 --- Jun. 2023}
    {
      \begin{cvitems}
        \item {Bank BTPN is the company behind Jenius, the first digital banking app in Indonesia with approximately 5 million users and 40 features. 
        I was trusted to manage a team of 18 developers, 12 quality assurances, and 2 quality engineers.}
        \item {Responsible for starting and designing the architecture of wealth management features in Jenius.}
        \item {Managed the team and collaborated with other organizations in the company to successfully release new features (investment, priority banking, insurance) in Jenius.}
        \item {Published developer guides of front--end coding conventions in Jenius.}
        \item {Collaborated with R\&D and developed internal libraries to implement distributed GraphQL architecture across microservices.}
        \item {Collaborated with an international partner for new integration and migration in Jenius and Sinaya in BTPN.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Engineer} % Job title
    {} % Organization
    {} % Location
    {Oct. 2019 --- Jun. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed architecture and developed full experiences for priority banking feature using React Native, Express.js, MongoDB, Apache Kafka, and Redis.}
        \item {Developed UI/UX components based on atomic design for Jenius front--end revamp with React Native.}
        \item {Developed Backoffice web app with ReactJS.}
        \item {Fixed vulnerability in Jenius app using React Native and native app development using Android Java and iOS Swift}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Front--end Developer (Part-time)} % Job title
    {FitHappy} % Organization
    {Central Jakarta, Indonesia} % Location
    {Apr. 2022 --- Sep. 2022} % Date(s)
    {
      \begin{cvitems} 
        FitHappy is a behavioral \& medical--based wellness startup backed by a top VC in Southeast Asia. 
        We help people to live healthier, lose weight, and solve chronic problems for good with digital habit--oriented program. 
        As a senior engineer, I initiate the front--end development best practices, code convention, and architectural patterns for the legacy codebase. 
        I also initiate the first release of FitHappy iOS app.
      \end{cvitems}
    }
    

%---------------------------------------------------------
  \cventry
    {Co-founder} % Job title
    {Edulens} % Organization
    {Bandung, Indonesia} % Location
    {May 2018 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        Edulens is a school management system app which digitalized school, parents, and teachers connections. 
        We also help students to prepare for university admissions with our services. 
        It received funding from campus through LPIK ITB and PMW ITB, also from Kemristekdikti through PKMI.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web and Mobile Developer} % Job title
    {Freelance} % Organization
    {Remote} % Location
    {May 2018 --- Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Received projects from local and international clients:}
        \item {Vessel Acceptance Modelling for Pertamina, Tanjung Sekong Terminal}
        \item {Social travel app for Piknik - Pitravelers}
        \item {Sales tracking app with GPS and camera functionality for Keboen23.com - Ixitask app}
        \item {Sales billing app with thermal printer functionality for Keboen23.com - Ixitask app}
        \item {A custom-made point-of-sale app for Lazise Catering, Sweden}
        \item {Publisher consultation app for Stanton Publishing House}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
